### 2023-05-07 writing/manuscript.Rmd
references update

---
header-includes:
- \usepackage[left]{lineno}
- \usepackage{mdframed}
- \usepackage{soul}
- \usepackage{xcolor}
- \definecolor{bleu}{HTML}{2200cc}
- \usepackage{caption}
- \usepackage{ragged2e}
- \usepackage{afterpage}
- \usepackage[labelformat = empty]{caption}
- \usepackage{rotating}
output: 
  pdf_document:
    fig_caption: yes
    number_sections: true
    latex_engine: xelatex
csl: apa.csl
bibliography: "citations.bib"
nocite: "@Bailey1988; @vanderHulst2010; @Inkelas1988; @Chen2016; Ngo2016; @Swaminathan2021; @Choi2021; @Evans2018a; @Jefferies1990; @Niesler2005; @Manyah2006; @Eme2022; @Westermeyer1977; @Hamann2015; @Goldsmith2011; @Ameka2001"
urlcolor: bleu
linkcolor: bleu
---

@@

Languages were primarily classified based on the World Atlas of Language Structures [@Maddieson2013] and the Lyon-Albuquerque Phonological Systems Database [@Maddieson2014]. Languages that are not present in either database were classified according to information from the Phonetics Information Base and Lexicon Database [@Moran2019] or other sources from the linguistics literature. A summary of all languages studied here, with further classification details and language-wise sample sizes, is in Table S1.

@@

Similarly, people with pitch perception deficits learn to compensate for their deficits by giving more weight to durational cues when decoding speech prosody [@Jasmin2020b; @Jasmin2020]. Recent evidence suggests that similar effects emerge in music perception: Mandarin speakers have difficulty *ignoring* pitch cues relative to English and Spanish speakers, who have been found to more frequently make decisions based on duration cues [@Jasmin2021]. In turn, this is consistent with theories of the overlapping mechanisms of basic auditory perception [@Patel2011; @Patel2012b; @Wong2007; @Tierney2013; @Peretz2015]. Our findings unite these results and show their generality.

>>>>

---
header-includes:
- \usepackage[left]{lineno}
- \usepackage{mdframed}
- \usepackage{soul}
- \usepackage{xcolor}
- \definecolor{bleu}{HTML}{2200cc}
- \usepackage{caption}
- \usepackage{ragged2e}
- \usepackage{afterpage}
- \usepackage[labelformat = empty]{caption}
- \usepackage{rotating}
output: 
  pdf_document:
    fig_caption: yes
    number_sections: true
    latex_engine: xelatex
csl: apa.csl
bibliography: "citations.bib"
nocite: "@Chen2016; Ngo2016; @Swaminathan2021; @Choi2021"
urlcolor: bleu
linkcolor: bleu
---

@@

Languages were primarily classified based on the World Atlas of Language Structures [@Maddieson2013] and the Lyon-Albuquerque Phonological Systems Database [@Maddieson2014]. Languages that are not present in either database were classified according to information from the Phonetics Information Base and Lexicon Database [@Moran2019] or other sources from the linguistics literature [@Ameka2001; @Bailey1988; @Eme2022; @Evans2018a; @Goldsmith2011; @Hamann2015; @Inkelas1988; @Jefferies1990; @Manyah2006; @Niesler2005; @vanderHulst2010; @Westermeyer1977]. A summary of all languages studied here, with further classification details and language-wise sample sizes, is in Table S1.

@@

Similarly, people with pitch perception deficits learn to compensate for their deficits by giving more weight to durational cues when decoding speech prosody [@Jasmin2020b; @Jasmin2021]. Recent evidence suggests that similar effects emerge in music perception: Mandarin speakers have difficulty *ignoring* pitch cues relative to English and Spanish speakers, who have been found to more frequently make decisions based on duration cues [@Jasmin2021]. In turn, this is consistent with theories of the overlapping mechanisms of basic auditory perception [@Patel2011; @Patel2012b; @Wong2007; @Tierney2013; @Peretz2015]. Our findings unite these results and show their generality.
